NeuronUnit: Validation Tests for Neurophysiology Models

### 2013-11-07 NeurounitFrontiers/Paper.tex
updated abstracted slightly

Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. 
Drawing inspiration from this practice, we developed the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against single empirical observations to produce a score indicating agreement between the model and the data. 
Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
Building on this framework, we describe here \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.

>>>>

Software engineers validate software by writing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
Suites of such unit tests can collectively provide evidence for its validity and correctness. 
Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against a single empirical observation to produce a score indicating agreement between the model and the data. 
Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
As a first application of this framework, we describe \textit{NeuronUnit}, a library that supports validation testing for neurophysiology and integrates with several existing neuroinformatics resources.
